\documentclass[12pt]{report}
\usepackage{geometry}
\usepackage{titling}

\geometry{margin=1in}

\newcommand{\subtitle}[1]{
	\posttitle{
		\par\end{center}
		\begin{center}\large#1\end{center}
		\vskip0.5em}
}

\title{Project Design and Direction}
\subtitle{CS 383 - Homework 1 - Group 3}

\author{
Mason Fabel \\
\and Morgan Holbart \\
\and Ronald Rodriguez \\
\and Tessa Saul \\
\and Lance Wells \\
\and Zachary Yama \\
}

\date{\today}

\begin{document}

\maketitle

\chapter{Individual Brainstorming}

\begin{section}{Mason Fabel}
Our project is to be ``a turn-based co-operative multiplayer
'dungeon-crawl' role-playing game'', combining the ideas of an adventurous
science fiction setting and the premise of a lowly office worker rising
through the ranks to become the master of his own destiny.

While contemplating these goals, I came up with a few central concepts and
observations I would like to see incorporated into the final project.

\begin{subsection}{Tone and Theme}
While there are a lot of directions the overall tone and feel of this
projecan take, I believe the best direction would be a lighthearted
combination of comedy, in the vein of Douglas Adam's Hitchhiker's Guide to
the Galaxy, and action/adventure, such as in Star Wars IV.

Taking this approach instead of a realistic approach gives the team more
freedom as to the shape of the final project. As we are not constrained by
accurately simulating reality, we can instead focus on creating a game that
is fun to play and avoid complicating areas that would not benifit from
such attentions.

Keeping a light tone will allow us to avoid dark or overly thoughtful
material. While this things have a time and a place, the purpose
of this project is to learn how to organize and create large pieces of
software, not to create an artistic or philosophical statement. By avoiding
such material, the focus is kept on the engineering, where it should be,
instead of the content, which is a matter for a different class.
\end{subsection}

\begin{subsection}{Content Generation}
The main purpose of this class is to learn software engineering, or how
to organize and build large software projects. While we have chosen to do
this in the form of a game, the purpose of this class is not game design,
but rather building a large application. Thus, whenever possible this
project should be moved away from creating game content and towards writing
code and organizing the development process.

To this end, I believe that as much game content should be generated on the
fly by the application wherever possible. This obviously covers simple
things, such as level layout, but it is not a hug jump of the imagination
to take this same aproach to many, if not all, of the elements that will
appear in the final product. Such examples may include NPCs, quest lines, or
equipment, but wherever we wish to have more than a handful of types this
sort of system is theoretically possible.

In addition to taking the burden of content generation away from the group
and giving it to the computer, this will have the further advantage of
allowing the size of the project to be scaled up (or down) by creating
different content generation methods for different sections of the final
game.

Finally, generating content will allow the final project, which is going to
be created by a small team in a short period of time, to have a lot of
content relative to programmer effort. Some finite amount of effort will
allow the final product to have a much larger amount of content, as
opposed to the more linear relationship involved when humans create
content by hand.
\end{subsection}

\begin{subsection}{NPC Social Networking}
Traditionally, most RPGs have used a system based upon levels and
experience points. While this works well in a lot of settings, it seems to
me that this transfers poorly over to the concept of the main character
being an office worker.

Thus, I would like to make progression in our final project not dependant
upone collect experience or gaining levels, but rather on a ``social
network'' of NPCs, for lack of a better term.

The basic idea is pretty simple. You have some ``relationship value''
with each NPC character. This value can be some positive or negative value,
with positive values meaning they like the player and a negative value
meaning they do not.

In addition to relating to the player, NPCs would relate to each other by
some percentage value between $-100\%$ and $100\%$. This would then serve
to modify the player's relationship with that NPC.

For example, the player has a $+50$ relationship with NPC A and a $-15$
relationship with NPC B. NPC A has a $10\%$ relationship with NPC B, and
NPC B has a $50\%$ relationship with NPC A. Thus, the player's final
relationship value with NPC A is $50+0.1(-15)=48.5$, and the player's
final relationship value with NPC B is $-15+0.5(50)=10$.

As the number of NPCs increases, a increasingly complex and interesting web
of characters can be created.

Now suppose that NPCs were tied to plot events or player progression.
Specifically, in order to advance further in the game, the player needs
to be promoted within the office or organization they work for, and this
can only be accomplished by gathering favor with their coworkers and
managers.

Furthermore, NPCs could be made to ignore the player until they reached
some relationship threshhold, thus causing the player to build relationship
with that NPS's ``friends'' in order to interact with them.

Finally, some method of gaining relationship with NPCs would need to be
implemented, whether a traditional ``kill 30 grues'' variety of quest or
some other, more original, method.

The result of this would be a varied and dynamic system (especially if this
network of NPCs was also generated by the game instead of being hard coded)
where the player is required to gain social goodwill until they finally
come to the attention of the top entities, thus recieving the final
promotion to CEO, or the final boss fight, or whatever the end game turns
out to be.
\end{subsection}

\end{section}

\begin{section}{Ronnie Rodriguez}
\begin{subsection}{Tone and Theme}
As my collegue has stated, a solid mix of humor and sci-fi action would be
an excellent direction to take the game in, especially since we have been
asked to keep the content ``G and PG'' rated. 

This begs the question, though, as to what brand of humor we should be
trying to use. In many comedic workplace-set films and TV shows, like The
Office, Office Space, Parks and Recreation, IT Crowd, etc., a palpable type
of sarcastic, droll, and deadpan humor is used. It's almost as if the
characters in these shows have just had all the life sucked out of them by
their boring, unfulfilling work, and almost everything that exits their
mouths is a bitter, sarcastic quip at something or someone. I think this
type of humor could translate well into a corporate-office set game. I
think it is entirely possible to do this, while keeping it PG rated. 
\end{subsection}

\begin{subsection}{Health Bar}
In many hack-n-slash RPG games, increasing in level gives you a bonus to 
your health bar. I think it would be cool to implement such a feature in
our game, but with a comedic twist. 

Assuming we adopt the deadpan style of humor popular in workplace-set
comedies populated by characters who, for all intents and purposes, seem to
have all but lost their will to go on, I think that instead of a ``health''
bar, it would be funny to have ``will to go on'' bar. 

For instance, instead of saying something like ``Health has been increased
by 5'' after going up a level, we could have something like ``Your will to
go on has slightly increased. So you got that going for you, which is
nice\ldots'' after our character receives a promotion within the company.
\end{subsection}
\end{section}

\begin{section}{Lance Wells}
The prompt in question asks that we merge two concepts:
\begin{itemize}
\item \emph{A Star-Warsish Sci-Fi in which you overthrow the evil empire}
\item \emph{A lowly office worker fending off paperwork and bureaucracy to challenge the CEO}
\end{itemize}

Blending the two ideas brings about a few questions:
Evil empire and a corporation to challenge? Why not work for the "bad guys"?
Paperwork to fend off and a Star-Warsish Sci-Fi setting? Why not fend off 
sentient paperwork?

I also have a general storyline-concept that I would like to propose:

\begin{center}
\emph{It's the year 272820 and the remnants of the human race have been
enslaved by the Conquesting and Expanding Organization, otherwise known as
the CEO.}
\end{center}

The only clear goal of the CEO is to mitigate the human spirit, and
assimilate the entirety of humanity into its dull corporation through the
most horrifying weapon imaginable: paperwork.

Maintaining a ``Will to Live'' (as per Ron's idea) is essential to surviving
the work-ridden future. Only by fighting the MAN (Malevolent Autonomous
Navigator), a super-intelligence deigned to direct the future of the Earth
towards a grim and monotonous future can the player(s) rescue the Earth and
avoid becoming soulless engines to a galactic war machine.
\end{section}

\begin{section}{Morgan Holbart Game Idea}
\begin{subsection}{Setting}
As a cooperative or, at least, multiplayer game, the story and overlying
setting of the game is not very important, I think the best blend of the
predetermined sci-fi and bureaucracy themes would simply place the player
in a world that combine the two with no overt explanation. For example,
the player is an office worker in an alien immigration building.
This gives a setting, a floor based ``dungeon'' (the building), and easily
changeable enemies. The enemies can be any assortment of the aliens that
come through the place, which means they can look like or do anything we
decide to fit the game, instead of trying to stick to a certain lore.
\end{subsection}

\begin{subsection}{Game Design}
The game will pit a player and his office colleagues into the immigration
office with the desire to exterminate all of the aliens currently inhabiting
the immigration office. You will work your way up starting from floor 1 to
the top floor where the main boss will be. Each floor will have a multitude
of mini bosses, enemies, loot rooms, and puzzles. Because of the procedural
generation, each game will have an entirely different flow. The player and
his colleagues should have to work together to solve each floor, finding and
killing the miniboss to unlock the next level, and completing any puzzles
to collect the superior loot to assist with the next floors.

Because the game is multiplayer, permadeath is a difficult feature to
implement, no one wants to wait for the game to end, so instead every time a
player dies, when the next floor is reached by his allies, he will be
revived with a reduced maximum health, if someone dies 3 or some number of
times, the next death will be permanent. Any ally can however revive a dead
player and sacrifice his maximum health to do so.

The game will feature a variety of weapons, the basic weapons will be the
human weapons, and will be the most common, you can find alien weaponry off
the corpses of your fallen foes which is the second tier of loot, and the
third tier of loot will drop from puzzles and mini bosses. All loot will be
tradeable between party members.

The progression system will be based purely on gear and floor number, there
is no need for an XP system, the enemies will scale with their floor, as
will the quality of loot drops.
\end{subsection}

\begin{subsection}{Game Technology}
The game should have several mechanics that function to enhance the game and
demonstrate our coding prowess. As a dungeon crawler, procedural generation
is a must. All levels of the game should be procedurally generated, as
should all items, possibly monster abilities/AI.

The game should adopt multiplayer systems for both LAN and internet based
gameplay, it can implement lobby based matchmaking, or direct IP connection,
but should not require an authoritative server for controlling game logic. 
This will leave the game open to hacking and potential cheating, but without
any leaderboards and the desire for LAN support, this should be a non issue.
Each client can most likely handle everything on its own, with one specific
host that will manage the communication between the two.

The game needs to have a sophisticated enough AI to support both
singleplayer play (bot controlled allies) and enemies with a alterable
difficulty to keep the challenge for players of all skill level. The AI
logic will have to be controlled by the host client.
\end{subsection}
\end{section}

\begin{section}{Game Direction – Zachary Yama}
\begin{subsection}{Story and Theme}
I very much like the story written by our first two game idea entires. Much
moreso than my own, but either way, here's my take on it.

The basic premise of our game must include both office worker themes and
sci-fi themes. The morphed combinational theme that comes to mind is of a
scientist who develops weapons of mass destruction for a company you, the
office worker, have deemed unethical and evil. The corruption of the company
you work for is so expansive that you dare not to leave out of fear.
However, because you aren’t the only scientist, you find yourself caught up
in the evil mad scientists’ scene when you really don’t want to be. The only
co-worker you’ve been friends with and ever enjoyed working with has
accidently unleashed an aggressive stimuli into the complex because of
reasons unknown. His dying act of kindness was to give you the only
vaccination. Your quest is to make it to ground level and out safely
(Underground working up? Tall building working down?), find out what
happened to your friend’s bio-aggression project, and wipe out all infected
individuals. All along the way you will be engineering and developing new
weapons, traps, and dispatching strategies to take out mobs, solve puzzles,
and defeat bosses.
\end{subsection}

\begin{subsection}{Building Weapons}
An additional feature that I would like to propose is the way weapons are
created and generated within the game. A good equipment system that feels
alive is something that can really bring a lot to the table. Though random
generation is an option, allowing the player to build something of their
very own is equally if not more powerful. It creates additional immersion
and charm to the game, and invites the player to continue somewhat soley for
the sake of finding out what new cool weapon they can build by defeating
the next enemy.

For weapons and items, having the ability to construct your own from parts
you've found throughout your adventures is extremely interesting. I've
seen this done before in the game Loadout, which is a free third person
shooter. It employs about 6 total parts for any weapon, which there are
about 10 varaiations of. Each part will modify the behavior of the weapon in
some way. For example, if you decided to use a scope you can zoom. If you
decide instead to use a lazer scope, now you've got a lazer to aim with. The
system would have to be altered to fit our game, but it wouldn't take that
much effort to come up with several weapon designs that are not only
customizable, but fun to play with. Having this kind of game element would
bring a lot of personal attachment with it, making the player more immersed.
The more fun the better, eh?
\end{subsection}
\end{section}

\begin{section}{Tessa Saul}
I would like to see a game where you can rebuild your character to test choices.
A lobby area where the player can arrearage the configuration of their 
modifications is a good match for that. In the lobby, the character cannot die,
or cannot take damage. The lobby also has `training dummy' type 
enemies that will persist through or reappear after player attacks. The lobby would allow
the player to test out new parts in a safe area so they can maximize their effectiveness.

In our group meetings, we talked about having the multi-player section of the game involve
dungeon areas. This means that you do storyline advancement on your own, and then get your
friends together to go fight off the bad-guys. We talked about the idea of going to cyberspace
to fight off viruses, which would be the dungeon area. I like this idea because it 
means that no-one actually dies, or gets hurt which is in line with the G or PG 
rating requirement. This idea is similar to a part of the game 
Shadowrun, where you also visit cyberspace to get secret information and fight viruses. In Shadowrun,
you get to load different helper programs, hardware, and tools to help you before you dive in. 
I think it would be fun to implement different equipment pieces like these. 

If we do a cyberspace centric game, I think it would be fun to gain skills in different programming languages,
and things we have learned about in class. That way your character can make their own viruses to 
match up against the bad ones, or implement better coding techniques to thwart the bad-guys. 
I think it would be easier to come up with jokes about this topic because we all already know about it. 
Overall, this idea is flexible, so I hope we can put a part of it in the game.
\end{section}

\chapter{Group Vision - Lance Wells}
% Please note that all of this is tenative and largely an artifact of
% storytelling, if you have any suggestions or changes, please make them.
% -- Lance Wells

I have decided to write this section in terms of fictional prose in an 
effort to more accurately describe the scenario without sounding too
laborious in the process.

\begin{section}{Setting - Lance Wells}
Nestled between the dusty bosom of Mars and the neo-genetic warlords of
Venus lies the glorious visage of Earth, a bustling, cybernetic utopia whose
chief export - human labor - drives the many corporate houses calling the
blue, green, and gray planet home.

One of the largest organizations on Earth, the Western Organization for
Resurgent Knowledge (W.O.R.K.) is your newest employer. White-washed,
colorless cubicles blanketed by flickering, fluorescent lights stretch for
miles as your sleepless coworkers dawdle about their systems.

Fortunately, escape from this bleak business purgatory is but keystrokes
away. As an Information Technology Associate (of the future), your primary
purpose in this business is to hunt-down and remove any pesky viruses
infecting the systems of your associates.

Neon-blue lines shift, pulsate, and shimmer as you enter the system of a
sales associate from cubicle 28xA1x47, Martha. Gradually coming into focus,
matrices of virtual wire outline your new surroundings. Walls and corridors
begin to form and shift into a gradually expanding labyrinth. Just as you
catch your breath, a dimly glowing red object comes into view, twitching
menacingly.

``A virus,'' you mutter to yourself as your right hand gradually shifts
downwards towards the weapon holstered on your e-belt. A lime-green,
glittering pistol reaches your fingertips. Pieced together meticulously from
parts won from previous conquests, its forking barrel snaps into action. As
you pull the trigger, four ``bit-lets'' jet towards the malware, twirling
into a tightly-closed circle, a signature of the Wrought-I/Orn hammer which
you so cleverly installed before this encounter.

Numerous foes follow, each torn apart by the partnership of your ruthless
trigger finger, and the weapon you endearingly refer to as ``Lucy''. Your
conquest ends, rather heroically, to be greeted by the familiar, boisterous
woman whose computer you have rid of the virtual invaders.

Left with the satisfaction of your coworker's appreciation, you feel your
efforts echoing across the cubicle space. Friends of your new ally, Martha,
now refer to you as a ``friend'', and promotions begin to feel inevitable.
Some day, you too aspire to face the mysterious figure at the head of
W.O.R.K., known to all as ``The C.E.O''.
\end{section}

\begin{section}{Story}

As a fresh-faced employee of the futuristic conglomerate known as
``W.O.R.K.'', your goal is to locate and destroy any viruses infecting the
systems of your coworkers. You, along with any other of your cohorts,
cleanse systems through the use of virtual reality. By cleaning each system,
you gain cybernated components for your digital arsenal in addition to 
the networked affections of your coworkers.

Your own intentions, however, lie with working your way up the corporate
ladder to eventually face the shadowy head of the company, ``The C.E.O.''.
A figure masked in infamy, little is known of The C.E.O. aside from the
effectual manner in which the company is run.

As you cut away infections from the workstations of your coworkers, the
source and origin of the malodorous programming slowly reveals itself. The
very same individual that determines the fate of your corporation is the one
distributing the electronic diseases.

Determined to stop this proliferation, you commit yourself to reaching the
corporate office and challenging your supervisor. System after system, your
skill as a malware-slayer grows in addition to the supply of friends that
begin to network and rally behind you.

Upon reaching the dark corporate ``castle'' of your dreaded executive
handler, you enter to discover that the sinister force behind the computer
plague is, itself, a computer. The final encounter of your journey, you
quickly adorn your virtual equipment and venture into the mainframe of the
baneful boss.

The swirling den of your former commander bids you death as you soon learn
that there is no easy solution to defeating this monster. A quick snippet of
code crafted by your affectionate coworkers materializes into a new shape
in your hands, the ``Information Terminator''. Like a magnet to a monitor,
you have but one option, you must lay the transmitter atop the C.E.O.'s 
sole weakness, the Malevolent Automation Node. As your mission becomes
clear, lights flash across your screen, ``To defeat this otherwise
impossible enemy, you must stick I.T. to the M.A.N.''.

The moment you strike the node with your transmitter, everything ceases to
move. All lights and motion slowly fall out of existence. Like black paint
flecked along a picture, the world around you gradually fades into
nothingness. Soon, all that is left is the booming voice of the former 
Computerized Executive Officer repeating ``ERROR: SYSTEM MALFUNCTION:
RECOMMEND REBOOT''. The cheers of your coworkers draw you back to reality,
their exuberance can only mean one thing. As shapes and colors return to
your vision, you glance at the monitor which had glared at you so
threateningly before. A happy face, composed of few pixels illustrates the
screen. Your victory is finally at hand.
\end{section}

\begin{section}{Mechanics}
For our game, we have decided to include several key features:
\begin{itemize}
\item \textbf{Weapon Creation System}\newline
	Our group has envisioned the weapons for our dungeon crawler to be 
	largely user-defined. By defeating dungeons, the user is able to piece 
	together various scraps and parts to form entirely new weaponry with 
	which to conquer a dungeon. While we have not discussed any hard-set 
	components, the concept maintains that the user will be able to craft 
	new items at a weapons terminal to take with them into instances.
	
\item \textbf{Dungeon Lobby and Dungeon Instancing}\newline
	Our imagined dungeon crawler will utilize a single "lobby" in which the 
	player is able to interact with their fellow office employees, group 
	together with other players, and create new weapons. The lobby in question 
	will resemble a modern office building, complete with grimy coffee stains 
	and irritating lighting.
	
	Entering a dungeon will consist of speaking with a given office worker, 
	and fulfilling their request to clean their system of a viral infestation. 
	Upon entering the ``dungeon'', the player will be joined by other players, 
	and will be able to begin hunting down and exterminating any rogue programs.
	
\item \textbf{Employee Networking}\newline
	Employees from our group vision are the entire source and lifeblood of the 
	office. Rather than implementing a generic leveling system, networking 
	with employees by completing specific quests and dungeons will grant the 
	player increased relations with that employee and any of their subsequent 
	friends. Forming a complex web, a player's coworker relations conceive a 
	unorthodox progression throughout the game, granting access to heretofore 
	unseen floors, areas, etc.
	
\end{itemize}
\end{section}

\end{document}
